Cover letter

### 2023-01-16 src/docs_review/cover.Rmd
First pass over Jeff's edits

Thank you for the opportunity to submit a revised version of our manuscript.
We appreciate the time you and the reviewers have given to providing helpful feedback.
Enclosed is a point-by-point response to all points raised.

>>>>

Many thanks for your consideration of our manuscript "Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa".
We appreciate the thoughtful comments from the reviewers and the opportunity to submit a revised version of our manuscript which incorperates the feedback.
Please find enclosed a point-by-point response to each of the reviewer's comments, and the editorial comments on journal requirements.
